Verifying Demonstrations

### 2020-03-13 paper/ZKPK.tex
Comments out SPK (not used in this paper)

When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
\begin{equation*}\label{SPKexample}
  \sigma\gets \SPK[\alpha, \beta, \gamma]%
  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
  [m],
\end{equation*}
which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).

>>>>

%When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
%\begin{equation*}\label{SPKexample}
%  \sigma\gets \SPK[\alpha, \beta, \gamma]%
%  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
%  [m],
%\end{equation*}
%(Signature based on Proofs of Knowledge) which yields a signature \(\sigma\) on 
%\(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = 
%g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).
